Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-08 vesicle_code/docs/adhesion/adhesion.tex
last edits for Feb 07 from yny

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
  \caption{\label{fig:extensional1} A doublet inside a fluid trap.  The
  reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} =
  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
  rate is $\chi = 0.02$.  The center of the vesicle, denoted with a
  black square, is a stagnation point.}

  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
  \caption{\label{fig:extensional2} A doublet inside a fluid trap.  The
  reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H}
  = 0.7$, the adhesion length scale is $\delta = 0.4$, and the
  extensional rate is $\chi = 0.07$.  The center of the vesicle, denoted
  with a black square, is a stagnation point.}

  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
  The reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} =
  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
  rate is $\chi = 0.1$.  The center of the vesicle, denoted with a black
  square, is a stagnation point.}

  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \caption{\label{fig:extensional4} A doublet broken by an extensional
  flow.  The reduced area is $\Delta A = 0.8$, the Hamaker constant is
  $\mathcal{H} = 0.7$, the adhesion length scale is $\delta = 0.4$, and
  the extensional rate is $\chi = 0.1$.  Initially, the doublet tilts to
  an inclination angle, and then the extensional rate overcomes the
  adhesive force and the doublet is broken.  The center of the vesicle,
  denoted with a black square, is a stagnation point.}
\end{figure}

@@

In Figures~\ref{fig:extensional1}--\ref{fig:extensional3},
snapshots of a fluid trap containing a vesicle doublet of reduced area
$\Delta A = 0.7$ are simulated at different extensional rates.  While
this doublet remains trapped around the stagnation point for all the
considered extensional rates, a doublet with a reduced area of $\Delta A
= 0.8$ is broken with an extensional rate $\chi = 0.1$
(Figure~\ref{fig:extensional4}).  We summarize the reduced areas and
extensional rates that result in a fluid trap in left plot of
Figure~\ref{fig:extensionalPhaseDiagram}. Parameter values with a blue
mark result in a fluid trap and parameter values with a red mark result
in vesicle separation.

For extensional rates and reduced areas that result in a fluid trap, the
initial configuration of the vesicles have the diverging stream
direction parallel to the vesicles' short axis.  Since the stable
configuration of two vesicles in an extensional flow has the converging
direction parallel to the vesicles' short axis, we expect the vesicles
to align themselves with the long axis parallel to the diverging
direction.  We observe in
Figures~\ref{fig:extensional1}--\ref{fig:extensional3} that the vesicles
do in fact rotate, but fall short of aligning their long axis with the
diverging direction.  We summarize the final inclination angle of the
doublet in the left plot of Figure~\ref{fig:extensionalPhaseDiagram}.
The size of the round dots are scaled to the final inclination angle as
defined in the right plot.  At smaller extensional rates, the vesicles
come closer to aligning their long axis with the diverging direction.
When the doublet is broken at reduced area $\Delta A = 0.80$, the
extensional rate is sufficiently large to align the long axis of the
vesicle with the diverging direction and then the vesicles separate
(Figure~\ref{fig:extensional4}).  For very low extensional rates, the
time horizon is insufficient for the doublet to reach an equilibrium
state, and these simulations are marked with a square.

\begin{figure}[htp]
%  \begin{minipage}{0.53\textwidth}
%    \includegraphics[width=0.33\textwidth]{figs/angleDefinition.pdf} \:
%    \includegraphics[width=0.34\textwidth]{figs/rotate1.pdf} \:
%    \includegraphics[width=0.26\textwidth]{figs/rotate2.pdf}
%  \end{minipage}
%  \hfill
  \begin{minipage}{0.45\textwidth}
    \centering
    \includegraphics[width=0.8\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \end{minipage}
  \caption{\label{fig:extensionalPhaseDiagram}  A phase diagram of the long-time
  behavior of a fluid trap formed by two adhering vesicles in an
  extensional flow.  The Hamaker constant is $\mathcal{H}=0.7$ and the
  adhesion length scale is $\delta = 0.4$.  For small extensional rates,
  the doublet structure is not broken (blue marks), while at large
  extensional rates, the doublet is broken (red marks).  The size of the
  round blue marks indicates the final inclination angle with the larger
  dots rotating less ($\theta=\pi$) and the smaller dots rotating more
  ($\theta = \pi/2$).  A square mark is used for simulations that did
  not result in an equilibrium inclination angle in the given time
  horizon.}
\end{figure}

In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
angle of the doublet as a function of time for four different
extensional rates (left) and the final inclination angle for all
doublets that reach an equilibrium state (right).  We observe that not
only do larger smaller extensional rates result in smaller inclination
angles, but smaller reduced areas also result in smaller inclination
angles.  Moreover, the critical Hamaker constant that determines if the
doublet remains trapped or is broken decreases with an increasing
extensional rate.

\begin{figure}[htp]
  \includegraphics[height=0.35\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \includegraphics[height=0.35\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
  inclination angle of a doublet formed by vesicles of reduced area
  $\Delta A = 0.7$ submerged in an extensional flow with an extensional
  rate of $\chi$.  {\em Right}: The final inclination angle of doublets.
  At larger extensional rates, the doublet is broken by the flow.
  Results are not reported for some of the low extensional rates since
  the doublet had not tilted to an equilibrium inclination angle for the
  given time horizon.}
\end{figure}

>>>>

@@

In Figures~\ref{fig:extensional1}--\ref{fig:extensional3},
snapshots of a fluid trap containing a vesicle doublet of reduced area
$\Delta A = 0.7$ are simulated at different extensional rates.  While
this doublet remains bound for all the
considered extensional rates, a doublet with a reduced area of $\Delta A
= 0.8$ is split with an extensional rate $\chi = 0.1$
(Figure~\ref{fig:extensional4}).  
%
For extensional rates and reduced areas that result in a bound vesicle doublet, 
we observe that the doublet always rotate from the $\theta=\pi/2$ configuration towards
the more stable $\theta=\pi$ configuration, as shown in Figures~\ref{fig:extensional1}--\ref{fig:extensional3}.
We also observe that in most cases with moderate extensional flow rates the doublet falls short of 
aligning their long axis with the diverging direction.

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}
  \caption{\label{fig:extensional1} A doublet inside a fluid trap.  The
  reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} =
  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
  rate is $\chi = 0.02$.  The center of the vesicle, denoted with a
  black square, is a stagnation point.}
  \end{figure}

  \begin{figure}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
  \caption{\label{fig:extensional2} A doublet inside a fluid trap.  The
  reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H}
  = 0.7$, the adhesion length scale is $\delta = 0.4$, and the
  extensional rate is $\chi = 0.07$.  The center of the vesicle, denoted
  with a black square, is a stagnation point.}
  \end{figure}

 \begin{figure}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
  The reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} =
  0.7$, the adhesion length scale is $\delta = 0.4$, and the extensional
  rate is $\chi = 0.1$.  The center of the vesicle, denoted with a black
  square, is a stagnation point.}
  \end{figure}

In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
angle of the doublet as a function of time for four different
extensional rates (left) and the final inclination angle for all
doublets that reach an equilibrium state (middle).  We observe that not
only do larger smaller extensional rates result in smaller inclination
angles, but smaller reduced areas also result in smaller inclination
angles.  Moreover, the critical Hamaker constant that determines if the
doublet remains trapped or is broken decreases with an increasing
extensional rate.
\begin{figure}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \caption{\label{fig:extensional4} A doublet broken by an extensional
  flow.  The reduced area is $\Delta A = 0.8$, the Hamaker constant is
  $\mathcal{H} = 0.7$, the adhesion length scale is $\delta = 0.4$, and
  the extensional rate is $\chi = 0.1$.  Initially, the doublet tilts to
  an inclination angle, and then the extensional rate overcomes the
  adhesive force and the doublet is broken.  The center of the vesicle,
  denoted with a black square, is a stagnation point.}
\end{figure}
We summarize the final inclination angle of the
doublet in the right plot of Figure~\ref{fig:extensionalInclinationAngle}.
The size of the round dots are scaled to the final inclination angle as
defined in the right plot.  At smaller extensional rates, the vesicles
come closer to aligning their long axis with the diverging direction.
When the doublet is broken at reduced area $\Delta A = 0.80$, the
extensional rate is sufficiently large to align the long axis of the
vesicle with the diverging direction and then the vesicles separate
(Figure~\ref{fig:extensional4}).  For very low extensional rates, the
time horizon is insufficient for the doublet to reach an equilibrium
state, and these simulations are marked with a square.
%
The right plot of Figure~\ref{fig:extensionalInclinationAngle} 
also summarizes the  reduced areas and
extensional rates that result in a bound vesicle doublet in a fluid trap: Parameter values with a blue
mark result in a fluid trap and parameter values with a red mark result
in vesicle separation.

%\begin{figure}[htp]
%  \begin{minipage}{0.53\textwidth}
%    \includegraphics[width=0.33\textwidth]{figs/angleDefinition.pdf} \:
%    \includegraphics[width=0.34\textwidth]{figs/rotate1.pdf} \:
%    \includegraphics[width=0.26\textwidth]{figs/rotate2.pdf}
%  \end{minipage}
%  \hfill
%  \begin{minipage}{0.45\textwidth}
%    \centering
%    \includegraphics[width=0.8\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
%  \end{minipage}
%  \caption{\label{fig:extensionalPhaseDiagram}  A phase diagram of the long-time
%  behavior of a fluid trap formed by two adhering vesicles in an
%  extensional flow.  The Hamaker constant is $\mathcal{H}=0.7$ and the
%  adhesion length scale is $\delta = 0.4$.  For small extensional rates,
%  the doublet structure is not broken (blue marks), while at large
%  extensional rates, the doublet is broken (red marks).  The size of the
%  round blue marks indicates the final inclination angle with the larger
%  dots rotating less ($\theta=\pi$) and the smaller dots rotating more
%  ($\theta = \pi/2$).  A square mark is used for simulations that did
%  not result in an equilibrium inclination angle in the given time
%  horizon.}
%\end{figure}

\begin{figure}[htp]
  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_ra070_inclinationAngle.pdf}
  \includegraphics[height=0.27\textwidth]{figs/adR4em1adS7em1_finalInclinationAngle.pdf}
  \includegraphics[height=0.27\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \caption{\label{fig:extensionalInclinationAngle} {\em Left}: The
  inclination angle of a doublet formed by vesicles of reduced area
  $\Delta A = 0.7$ submerged in an extensional flow with an extensional
  rate of $\chi$.  {\em Middle}: The final inclination angle of doublets.
  At larger extensional rates, the doublet is broken by the flow.
  {\em Right}: A phase diagram of the long-time
  behavior of a fluid trap formed by two adhering vesicles in an
  extensional flow.
  Results are not reported for some of the low extensional rates since
  the doublet had not tilted to an equilibrium inclination angle for the
  given time horizon.}
\end{figure}
